---
title: 'Dynamic Joint Learner: Analysis on Sensitivity to F'
output:
  pdf_document: default
  html_document:
    df_print: paged
header-includes:
  - \usepackage{subcaption}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# The analysis scripts use paths relative to the code directory.
# Therefore, the working directory is set to the code directory.
knitr::opts_knit$set(root.dir = file.path(getwd(), "code"))
```



```{r, include=FALSE}
# Libraries for running in parallel
library(doParallel)
library(foreach)
library(kableExtra)
library(knitr)
library(tibble)


# Import the functions for generating data, running the model, and obtaining results
source("model_generation_running_and_testing_functions.R")
source("F_sensitivity_results_function.R")
```


## Configuration of the Simulation


We conduct a sensitivity analysis to assess the effect of the
number of NN-GP layers, $F$, used to fit the Dynamic Joint Learner.
The data are generated under three configurations of the true
latent dimension $R^*$ and number of NN-GP layers $F^*$:
$(R^*,F^*) \in \{(4,1),(3,2),(2,3)\}$.

For each configuration, we fit the model using
$F \in \{1,2,3,4\}$ NN-GP layers and summarize performance using AUC, MSPE, $95\%$ PI coverage and length over over three simulation replications.

```{r}

# NN-GP Data Generation Simulation Values used in each of the three cases

# Number of Graph Layers
L = 2

# Number of nodes in the graphs on each layer
J = 20

# Number of attributes for each node
m = 2

# Number of time points (with one being out-of-sample)
T_len = 21


# Hyperparameters for NN-GP Data Generation in Cases 1,2, and 3 

# True dimensions of latent vectors used for data generation, R*
R_vals = c(4, 3, 2)

# True number of NN-GP layers used for data generation, F*
sim_F_vals = c(1, 2, 3)

# Concatenate the corresponding true R and F values into a list of vectors
R_and_sim_F_vals = I(list(c(R_vals[1], sim_F_vals[1]), 
                          c(R_vals[2], sim_F_vals[2]), 
                          c(R_vals[3], sim_F_vals[3])))


# Values for F, the number of NN-GP layers, used to fit DJL in each case
# of the sensitivity analysis
fitted_F_vals = c(1:4)

# Random seeds for the replications of each case
seed_vals = c(22, 25, 26)


# Create a grid using the true R and F for each case, the value of F used to fit DJL,
# and the values for the seeds in each replication
param_grid = expand.grid(R_and_sim_F_vals = R_and_sim_F_vals,
                   fitted_F = fitted_F_vals,
                   seed = seed_vals)


# Number of MCMC iterations used to fit DJL
niter = 3000

# Number of iterations to discard as burn-in after fitting DJL
n_burn_in = 2000




# Dimension of the latent vectors used for fitting DJL
fitted_R = 4

```

## Run the Simulations

The following code runs the different simulations in parallel and saves the results.

```{r run-simulation, results='hide', message=FALSE, warning=FALSE}

# Create a directory named "outputs" to store results if it does not already exist
if (!dir.exists("outputs")) {
  dir.create("outputs")
}


# Configure parallel R environment

# Number of cores to use, if left equal to NULL, all available cores will be used
n_workers = 6

if (is.null(n_workers)) {
  n_workers = detectCores()
}

print(paste("Number of cores: ", n_workers, sep = ""))

cl <- makeCluster(n_workers) 
registerDoParallel(cl) 



parallel_runs <- foreach (case = 1:nrow(param_grid)) %dopar% {
  
  source("model_generation_running_and_testing_functions.R")
  

  cur_params = param_grid[case, ]
  

  
  model_generation_running_and_testing(L = L, J = J, m = m, T_len = T_len,
                                       R = cur_params$R_and_sim_F_vals[[1]][1],
                                       time_grid = seq(from = 1, to = T_len, length.out = T_len),
                                       time_props_missing = rep(0.1, L),
                                       edge_props_missing = rep(0.25, L), nngp_gen = TRUE,
                                       tergm_gen = FALSE,
                                       nngp_L = cur_params$fitted_F,
                                       sim_nngp_L = cur_params$R_and_sim_F_vals[[1]][2], 
                                       sigma2_w = 0.4,
                                       sigma2_b = 0.01,
                                       niter = niter, fitted_R = fitted_R,
                                       fitted_R_zeta = fitted_R,
                                       seed = cur_params$seed,
                                       n_burn_in = n_burn_in, n_thinning = 1,
                                       remove_last_point = TRUE)

}
  
  
stopCluster(cl)


```


## Aggregate the Results

The section of the code aggregates the results from the simulation replications for $F\in\{1,2,3,4\}$ in Case 1, Case 2, and Case 3, respectively.

```{r}

# Aggregated results for Case 1 with R* = 4, F* = 1
results_case_1 = F_sensitivity_results(fitted_F_vals = fitted_F_vals,
                                       fitted_R = fitted_R,
                                       seed_vals = seed_vals,
                                       L = L, J = J, m = m,
                                       R = R_vals[1],
                                       sim_F = sim_F_vals[1],
                                      T_len = T_len, niter = niter, n_burn_in = n_burn_in) 

# Add F heading
results_case_1 <- lapply(results_case_1, function(df) {
  df <- as.data.frame(df)
  df <- rownames_to_column(df, var = "F")
  df
})



# Aggregated results for Case 2 with R* = 3, F* = 2
results_case_2 = F_sensitivity_results(fitted_F_vals = fitted_F_vals,
                                       fitted_R = fitted_R,
                                       seed_vals = seed_vals,
                                       L = L, J = J, m = m,
                                       R = R_vals[2],
                                       sim_F = sim_F_vals[2],
                                       T_len = T_len, niter = niter, n_burn_in = n_burn_in) 

# Add F heading
results_case_2 <- lapply(results_case_2, function(df) {
  df <- as.data.frame(df)
  df <- rownames_to_column(df, var = "F")
  df
})

# Aggregated results for Case 3 with R* = 2, F* = 3
results_case_3 = F_sensitivity_results(fitted_F_vals = fitted_F_vals,
                                       fitted_R = fitted_R,
                                       seed_vals = seed_vals,
                                       L = L, J = J, m = m,
                                       R = R_vals[3],
                                       sim_F = sim_F_vals[3],
                                       T_len = T_len, niter = niter, n_burn_in = n_burn_in) 

# Add F heading
results_case_3 <- lapply(results_case_3, function(df) {
  df <- as.data.frame(df)
  df <- rownames_to_column(df, var = "F")
  df
})

```


## Simulation Results

The following tables summarize the results for sensitivity to $F$ in Case 1, Case 2, and Case 3, respectively.



\begin{table}[ht]
\caption{AUC, MSPE, and $95\%$ Prediction Interval Coverages and Lengths for different values of $F$ used to fit DJL in the in-sample, missing, and out-of-sample predictive scenarios in Case 1. Here, we use $L = 2$, $J=20$, $T=20$, $m = 2$, $R^* = 4$, and $F^* = 1$ for data generation. DJL is fitted with $R = 4$. Note. These results correspond to Table 8 in the supplementary materials.}
\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_1$auc_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{AUC for Edge Prediction}
\end{subtable}%
\hfill
\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_1$mspe_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{MSPE for Nodal Attribute Prediction}
\end{subtable}%

\vspace{2em}

\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_1$cov_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{95\% Prediction Interval Coverage}
\end{subtable}%
\hfill
\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_1$len_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{95\% Prediction Interval Length}
\end{subtable}
\end{table}



\begin{table}[ht]
\caption{AUC, MSPE, and $95\%$ Prediction Interval Coverages and Lengths for different values of $F$ used to fit DJL in the in-sample, missing, and out-of-sample predictive scenarios in Case 2. Here, we use $L = 2$, $J=20$, $T=20$, $m = 2$, $R^* = 3$, and $F^* = 2$ for data generation. DJL is fitted with $R = 4$. Note. These results correspond to Table 9 in the supplementary materials.}
\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_2$auc_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{AUC for Edge Prediction}
\end{subtable}%
\hfill
\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_2$mspe_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{MSPE for Nodal Attribute Prediction}
\end{subtable}%

\vspace{2em}

\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_2$cov_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{95\% Prediction Interval Coverage}
\end{subtable}%
\hfill
\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_2$len_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{95\% Prediction Interval Length}
\end{subtable}
\end{table}



\begin{table}[ht]
\caption{AUC, MSPE, and $95\%$ Prediction Interval Coverages and Lengths for different values of $F$ used to fit DJL in the in-sample, missing, and out-of-sample predictive scenarios in Case 3. Here, we use $L = 2$, $J=20$, $T=20$, $m = 2$, $R^* = 2$, and $F^* = 3$ for data generation. DJL is fitted with $R = 4$. Note. These results correspond to Table 10 in the supplementary materials.}
\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_3$auc_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{AUC for Edge Prediction}
\end{subtable}%
\hfill
\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_3$mspe_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{MSPE for Nodal Attribute Prediction}
\end{subtable}%

\vspace{2em}

\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_3$cov_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{95\% Prediction Interval Coverage}
\end{subtable}%
\hfill
\begin{subtable}{.45\linewidth}
\centering
```{r, echo=FALSE}
kable(results_case_3$len_df, format="latex", booktabs=TRUE, digits=4)
```
\caption{95\% Prediction Interval Length}
\end{subtable}
\end{table}

